Contextual Combinatorial Cascading Bandits

### 2015-12-09 contextual combinatorial cascading bandits.tex
update proofs of lemma 4.9 and main theorem

\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

@@

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
	\label{eq:functionf}
\end{align}
Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
\begin{align*}
A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
$$
where $R(t, \bA_t) = f_t^{\ast} - f(\bA_t, \theta_{\ast}^{\top}x_t)$.

@@

If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
 (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
 \label{eq:functionfstar}
\end{align}
then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. To simplify notations, we assume 
$$
\gamma_k' = 1 - \gamma_k.
$$
Then it holds that
\begin{equation}
\label{eq:ConDisRelation}
f_{\wedge}(A, w) = 1 - f(A, 1 - w).
\end{equation}
Let 
\begin{align*}
A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
$$
where $R_{\wedge}(t, \bA_t) = f_{\wedge, t}^{\ast} - f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$.

@@

\begin{theorem}[\cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
%$$
%\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
%$$
%\wei{I thought the following is simpler. Should we use the following?}
$$
\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}.
$$
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\label{eq:estimateTheta}
\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \beta_{t}(\delta).
\end{equation}
\end{theorem}

This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm. Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
\begin{equation}
\label{eq:defU}
\bU_t(a) = \min\left\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1 \right\}.
\end{equation}

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma}
\label{lem:estimateU}
When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
$$
0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. 
First, the learning agent 
	computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. 
Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like
 $\begin{pmatrix} A\\ B\end{pmatrix}$.

\begin{algorithm}
\caption{C$^3$-UCB}
\label{alg:ConComCascade}
\begin{algorithmic}[1]
\STATE {//Initialization}
\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
%\STATE{}

@@

\STATE {//Compute UCBs}
\STATE {$\forall a\in E: $}
\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
%\STATE {}

@@

\STATE {//Update statistics}
\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
\ENDFOR {~~$t$}
\end{algorithmic}
\end{algorithm}

@@

To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R(t, \bA_t)|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
\begin{lemma}
\label{lem:DeltaEstimate}
For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
$$
R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
$$
if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
$$
R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}

@@

%\begin{lemma}
%\label{lem:prefixExist}
%Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
%$$
%p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t).
%$$
%\end{lemma}
From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $R_{\wedge}(t, \bB_t)$ will not be too small. Then follow the above deductions, we can get a good estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$. Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$, thus for $R_{\wedge}(T)$. We leave all details in the next subsection.
}

@@

The following lemma provides the important result on the regret at each time $t$
	in terms of feature vectors of base arms at the time.
\begin{lemma}
	\label{lem:DeltaEstimate}
	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
	$$
	R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
	$$
	if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
	$$
	R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
	$$
\end{lemma}
\begin{proof}
By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
$$
f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
$$
By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
$$
f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
$$
f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
The result for the conjunctive case can be deduced in a similar way.
\end{proof}

@@

@@

Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. However, $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ is hard to estimate because $\bV_t$ only contains observed base arms. So we need the following lemma.
\begin{lemma}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. For any time $t$ and the chosen action $\bA_t = (\ba_1^t, \ldots, \ba_{\abs{A}}^t )$, we have $f(A_t^*, \bU_t) \leq f(A, \bU_t)$. Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
$$
E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE\left[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE\left[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right].
\end{align*}
\end{lemma}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

>>>>

\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

@@

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
	\label{eq:functionf}
\end{align}
Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
\begin{align*}
A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
$$
where $R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t)$.

@@

If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
 (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
 \label{eq:functionfstar}
\end{align}
then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. To simplify notations, we assume 
$$
\gamma_k' = 1 - \gamma_k.
$$
Then it holds that
\begin{equation}
\label{eq:ConDisRelation}
f_{\wedge}(A, w) = 1 - f(A, 1 - w).
\end{equation}
Let 
\begin{align*}
A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
$$
where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.

@@

\begin{theorem}[\cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
%$$
%\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
%$$
%\wei{I thought the following is simpler. Should we use the following?}
$$
\bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}.
$$
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\label{eq:estimateTheta}
\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
\end{equation}
\end{theorem}

This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\bbeta_t(\delta)$ under $\bV_t$ norm. Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
\begin{equation}
\label{eq:defU}
\bU_t(a) = \min\left\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1 \right\}.
\end{equation}

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma}
\label{lem:estimateU}
When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
$$
0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. 
First, the learning agent 
	computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. 
Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like
 $\begin{pmatrix} A\\ B\end{pmatrix}$.

\begin{algorithm}
\caption{C$^3$-UCB}
\label{alg:ConComCascade}
\begin{algorithmic}[1]
\STATE {//Initialization}
\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
\STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
%\STATE{}

@@

\STATE {//Compute UCBs}
\STATE {$\forall a\in E: $}
\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
%\STATE {}

@@

\STATE {//Update statistics}
\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
\STATE {$\bbeta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
\ENDFOR {~~$t$}
\end{algorithmic}
\end{algorithm}

@@

To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R(t, \bA_t)|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
\begin{lemma}
\label{lem:DeltaEstimate}
For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
$$
R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
$$
if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
$$
R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}

@@

%\begin{lemma}
%\label{lem:prefixExist}
%Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
%$$
%p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t).
%$$
%\end{lemma}
From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $R_{\wedge}(t, \bB_t)$ will not be too small. Then follow the above deductions, we can get a good estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$. Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\bbeta_{t-1}(\delta)$, we can get an estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$, thus for $R_{\wedge}(T)$. We leave all details in the next subsection.
}

@@

@@

The following lemma provides the important result on the regret at each time $t$ in terms of feature vectors of base arms at the time.
\begin{lemma}
\label{lem:DeltaEstimate}
For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
$$
R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
$$
if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
$$
R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
$$
f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
$$
By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
$$
f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
$$
f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
The result for the conjunctive case can be deduced in a similar way.
\end{proof}

@@

Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. However, $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ is hard to estimate because $\bV_t$ only contains observed base arms. So we need the following lemma.
